Type Error Telemetry at Scale

### 2023-09-22 programming23/paper.tex
delete stochastic, use 'QALAN' instead of 'FILL Alan'

\title{Type Error Telemetry at Scale: Pseudonymized and Stochastic}
% lean, lite, modest, non-intrusive, private, ...
% {Millions of Type Errors} = 72M forced strict, 1/2M type error is disappointing!
%% \subtitle{Impersonal Telemetry to Measure User Experience}

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\percentile}[1]{{#1}th~percentile}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\stddev}[1]{[#1\textsc{k}]}
\newcommand{\gcell}[1]{\cellcolor{green!20}#1}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}
\newcommand{\gbox}[1]{\colorbox{green!20}{#1}}
\newcommand{\ybox}[1]{\colorbox{yellow!18}{#1\vphantom{Ap}}}
\newcommand{\obox}[1]{\colorbox{orange!29}{#1\vphantom{Ap}}}
\newcommand{\rbox}[1]{\colorbox{red!30}{#1\vphantom{Ap}}}
\newcommand{\tefsfont}[1]{\textsc{#1}}
\newcommand{\tekey}{\tefsfont{te}}
\newcommand{\fskey}{\tefsfont{fs}}

@@

{Roblox Studio} has a telemetry system, which is used to gauge
the effectiveness of creation features. This system stochastically
determines which sessions should report telemetry, and for those
sessions, reports telemetry records back with a summary of the
session. In the case of this study, the telemetry includes data on the
number of errors at various levels of granularity: in the current edit
range, in the current file, and in every file which was type
checked.

@@

  \item
    \FILL{} which errors break the Drop > Add > Keep hope?

  \item
    (NOTE may want to save relative popularity for next section.)
    Some errors occur more often in \mnonstrict{} than \mstrict{}:
    \code{CannotCallNonFunction},
    \code{CannotExtendTable},
    \code{ExtraInformation},
    \code{FunctionDoesNotTakeSelf},
    \code{IllegalRequire},
    \code{ModuleHasCyclicDependency},
    \code{OptionalValueAccess},
    \code{UnknownPropButFoundLikeProp}.
    \FILL{} is this surprising, or expected from the bigger number of
    \mnonstrict{} records?

@@

  \item
    Four errors from the \mnonstrict{} records never appeared in \mstrict{} mode:
    \code{DuplicateTypeDefinition}, \code{OnlyTablesCanHaveMethods},
    \code{MissingUnionProperty}, and \code{FunctionDoesNotTakeSelf}.
    (\FILL{} Alan is this interesting, or just a result of having less strict data?)

@@

\FILL{} I (ben) think we need to talk more about forced strict errors here, or soon.
Otherwise people will forget they exist in the data.
(But if they're not useful to us, remove them!)

>>>>

\title{Type Error Telemetry at Scale}
% lean, lite, modest, non-intrusive, private, ...
% {Millions of Type Errors} = 72M forced strict, 1/2M type error is disappointing!
%% \subtitle{Impersonal Telemetry to Measure User Experience}

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\percentile}[1]{{#1}th~percentile}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\stddev}[1]{[#1\textsc{k}]}
\newcommand{\gcell}[1]{\cellcolor{green!20}#1}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}
\newcommand{\gbox}[1]{\colorbox{green!20}{#1}}
\newcommand{\ybox}[1]{\colorbox{yellow!18}{#1\vphantom{Ap}}}
\newcommand{\obox}[1]{\colorbox{orange!29}{#1\vphantom{Ap}}}
\newcommand{\rbox}[1]{\colorbox{red!30}{#1\vphantom{Ap}}}
\newcommand{\tefsfont}[1]{\textsc{#1}}
\newcommand{\tekey}{\tefsfont{te}}
\newcommand{\fskey}{\tefsfont{fs}}
\newcommand{\QALAN}{\FILL{} Alan:}

@@

{Roblox Studio} has a telemetry system, which is used to gauge
the effectiveness of creation features. This system randomly
determines which sessions should report telemetry, and for those
sessions, reports telemetry records back with a summary of the
session. In the case of this study, the telemetry includes data on the
number of errors at various levels of granularity: in the current edit
range, in the current file, and in every file which was type
checked.

@@

  \item
    \FILL{} which errors break the Drop > Add > Keep ``preferred order''?

  \item
    (NOTE may want to save relative popularity for next section.)
    Some errors occur more often in \mnonstrict{} than \mstrict{}:
    \code{CannotCallNonFunction},
    \code{CannotExtendTable},
    \code{ExtraInformation},
    \code{FunctionDoesNotTakeSelf},
    \code{IllegalRequire},
    \code{ModuleHasCyclicDependency},
    \code{OptionalValueAccess},
    \code{UnknownPropButFoundLikeProp}.
    \QALAN{} are any of these surprising, or expected from the bigger number of
    \mnonstrict{} records?

@@

  \item
    Four errors from the \mnonstrict{} records never appeared in \mstrict{} mode:
    \code{DuplicateTypeDefinition}, \code{OnlyTablesCanHaveMethods},
    \code{MissingUnionProperty}, and \code{FunctionDoesNotTakeSelf}.
    (\QALAN{} is this interesting, or just a result of having less strict data?)

@@

\FILL{} I (ben) think we need to talk more about forced strict errors here, or soon.
Otherwise people will forget they exist in the data.
